### 2009-11-10 doc/tech_doc/infosys/infosys_technical.tex
Replacing 'Security Framework of ARC1' with 'ARC Security Framework (NORDUGRID-TECH-16)'

\textit{This section extensively uses terms defined in "Security Framework of WS-ARC" document"~\cite{arcsec}.}

@@

\textit{For information about sophisticated authorization policies and how to deploy various Policy Decision Point entities please see "Security Framework of WS-ARC" document"~\cite{arcsec}.}

>>>>

\textit{This section extensively uses terms defined in "ARC Security Framework (NORDUGRID-TECH-16)" document"~\cite{arcsec}.}

@@

\textit{For information about sophisticated authorization policies and how to deploy various Policy Decision Point entities please see "ARC Security Framework (NORDUGRID-TECH-16)" document"~\cite{arcsec}.}
